\section{The Martinist Visualization \& Prayer}
It should be done daily: on awakening; on getting ready for sleep at night, and many
times during the day.

Be comfortable. Close your eyes if circumstances allow, relax and breathe easily. Visualize yourself in your alb\ldots see it radiantly white\ldots call to mind its meaning --- the Original Robe of Glory --- purity.

Put on your Cordelier, symbol of the Magic Circle and the Traditional Chain. It reminds you of your linkage to your Initiator, to all others in the Chain of Light, and to the Source of Light Itself.

Now enfold yourself in your mystical black cloak. It renders you insensitive to the attacks of the base powers of ignorance. Through its use, you enter easily into meditation\ldots you ``go within'' and commune with your innermost self, which knows all.

Lastly, don your mask\ldots the most powerful tool for the development of the true mystical personality. Through its use, you subjugate the petty ego and protect yourself from the undesirable aspects of your mundane personality, such as pride, conceit, vanity and arrogance

Visualize above yourself the flaming Pentagram.

Mentally review yourself now, clearly see yourself completely dressed in your habiliments\ldots \textit{actually feel} them about you. See the flaming pentagram above you and \textit{hear} the flames hissing --- \textit{feel} their warmth.

Now silently, or very softly, intone the Name \textit{Ieschouah} (``yea-hesh-shoe-wah'') one or more times.

After a short period, using your feeling nature, strive to be \textit{en rapport} with the Past Masters and all brethren in the Initiatic Chain. Call to mind someone near and dear to you: a family member, a friend, a world leader, a nation or group of people, or someone you wish to help. Visualize them fully clothed in the vestments. Visualize the Pentagram flaming above them, and again intone the Name \textit{Ieschouah} one or more times (either silently or softly) and send them thoughts of love.

\begin{quote}{Remember}
The Higher Powers care little for the shallow values of the profane world, but everything for love, brotherhood, kindliness charity, humility, sincerity, beneficence, consolation, and compassion.
\end{quote}

Never neglect the Martinist Visualization \& Prayer. It is a prayer of the strongest potency. Let it be a routine, several times daily: an essential practice of your Martinist Way of Life. Use this Mystic practice as you move through the day, silently blessing all those whom you observe to be saddened, distraught, sick, or in need. Your meditations will indicate to you how to use this visualization and prayer in other ways.