%\section{Introduction}
%
\moupyell{} (or \moup{}) is an initiatory Order open to all men and women of good will who:

\begin{itemize}
    \item wish to bring down the Kingdom of God by the awakening and by the more intense communion with the message and the life of the Glorious Christ whom they feel in their deep inner being;
    \item believe that the coming of this Kingdom is at first governed by a personal spiritual activity, the aim of which is to blossom in the middle of daily life the qualities of heart and spirit with which they are entrusted with;
    \item believe in finding a source of spiritual nourishment in the study of the sacred books and of the human thoughts found in hermetic traditions, philosophy and science;
    \item believe in the help of the ``Passed Masters,'' such as the Rose+Cross, Pythagoras, Plato, Plutarch, Master Eckhart, Jacob Boehme, Swedenborg, Eckhartshausen, Martinez de Pasqually and his disciples Louis-Claude de Saint-Martin, Master Phillip of Lyon, as well as all those who inspired them or who were inspired by them ever after;
    \item believe that the blossoming of the inner being results from a path which, although distinctive to everybody, however needs an initiation and a support, which will be found easier in an already existing spiritual community;
    \item believe that now, at the beginning of the Aquarian age, humanity having changed, the conditions of life and specially its rhythm having changed, it is time to prepare us inwardly to receive and to transmit the new energies which will take us to a state of more elevated consciousness, to new responsibilities and to more efficient actions in the midst of the Creation.
\end{itemize}

The aim of the Order is the Reintegration of the Human Being into his/her
primitive purity, the ever more and more approaching of mankind to God. \mouplong{} is one of the
branches of the prestigious filiation mentioned above. It transmits, with complete
regularity, through initiatory filiation, the traditional degrees of Martinism. The
Order admits in its ranks men and women who wish to work in complete
brotherhood/sisterhood for their spiritual evolution in an ascending movement
towards the Creating Principle.

\begin{quote}
    The aim to attain is and will always be the spiritualisation of individuals and societies.
\end{quote}
\begin{flushright}
    --- Joanny Bricaud,\\\textit{Notice Historique sur le Martinisme}
\end{flushright}

In this regard let us mention the following words written by \textbf{PAPUS}:

\begin{quote}
    The Order, in its whole, is above all a school of moral chivalry, trying hard
to develop spirituality in its members by the study of the invisible world and its
laws, by the exercise of devotion and of intellectual assistance, and by the creation
in each spirit of a faith, all the more solid because it is based on observation and
science. Martinism derives directly from Christian Illuminism and has adopted its
principles.
\begin{itemize}
    \item Forming the real centre of this living University, that will one day
recreate the marriage without division of Science and Faith, without epithet,
Martinism tries to be worthy of this name by establishing superior schools of
metaphysical and physiological science, disdainfully moved away from classical
teachings under the pretext that it is occult.
    \item Our epoch of scepticism, of
adoration of the material world and of atheism, needed so badly a frank Christian
reaction, independent of all clergies, that in all the countries where it has
penetrated, Martinism has saved many souls from doubt, despair and suicide. It
brought back to the comprehension of Christ many spirits that certain clerical
actions had moved away from Faith.
    \item Not asking from its members any
contribution, nor entrance fees into the Order, neither asking any regular tribute
from the Lodges to the Supreme Council, Martinism has remained faithful to its
spirit and origins by making material poverty its very first rule.
    \item Martinists want
to be Christians, free from any clerical connection, and the accusations of
``Satanism'' will just make them shrug their shoulders, while asking Heaven for
mercy for those who slandered them unfairly.
    \item Martinists do not practise any
magic, be it white or black. They study, they pray and they forgive injustices.
    \item Martinism does not ask its members for any oaths of passive obedience, nor does
it impose on them any dogma, be it materialistic or clerical, thus leaving them in a
perfect freedom of consciousness.
    \item \ldots We simply remain fervent Knights of
Christ, enemies of violence and vengeance, resolute synarchists, opposed to any
anarchy from above or below, in one word, Martinists, as have been our glorious
ancestors Martines de Pasqually, Claude de Saint-Martin and Willermoz!
\end{itemize}
\end{quote}

\mouplong{}, wanting itself free from any Saturnian structure, hardly has any organised structure, this means, there are no statutes, no registered office, no membership cards, no subscription fees, no entrance fees. It exists only in the Invisible.

It consists of simple adherents and of ``Initiates'' divided in three grades, two
probationary degrees and one grade. This grade, the \si{} or ``Unknown
Superior'' (also called ``Unknown Server'') is only granted to members who show
themselves worthy by their behaviour in their daily life, as well as by their special
knowledge (concerning the doctrine and workings of the ``Passed Masters'' of
Martinism --- hermetic traditions) and in general by their support for Martinist
principles. Only the grade of \si{} can under certain conditions grant the right
and the power to initiate according to the Tradition.

\moup{} is constituted of two Circles:

\begin{enumerate}[label=\alph*)]
    \item the \textbf{External Circle} for esoteric studies, which is a school of instruction for the first two degrees which meet in an ``Instruction Lodge,''
    \item The \textbf{Inner Circle} of the SS\hexdot{}II\hexdot{} who meet in a ``Chapter'' or ``Grand Chapter'' and whose will is to be part of this chosen community called the ``Inner Sanctuary,'' ``Society of the Elect'' or ``Inner Church'' (D’Eckhartshausen and Lopoukhine), which is aware of the universal and central character of esoterism and for which ``the present possession of God, of Jesus-Christ in us, is the centre to which all mysteries, as the rays of a circle, focus.'' (D’Eckhartshausen, \textit{La Nuée sur le Sanctuaire}).
\end{enumerate}

Martinism is Christian chivalry, or, if preferred, a chivalric line of individual and
collective improvement. It thus must tend to be made up only of perfect servers
and successors of the real Masters of the movement.

This asks all members for a pattern of behaviour freely accepted by all, a spirit of
devotion and a discipline without which all the collective work would be
impossible. Greatest tolerance or better, widest spirit of comprehension is thus
required.

We so ask you to meditate on your request and to find out the deeper reasons of it,
according to these indications, before taking any further steps.
If you want more information or if you want to become a member of our Order,
please contact us at \url{www.moup.org}.