\section[A Concise History of MOUP for its Members]{A Concise History of the Martinist Order of Unknown Philosophers for its Members}

Most Ill\hexdot{} Brother Michael N. Buckley, ``Fidentia,'' Grand Master, \sigi{}

\subsection{Origins}

The formation of a Martinist Grand Lodge is very often shrouded in mystery as to how such a
body actually came into existence. There are complex reasons for this and time and second hand
historical reporting often adds to the sense of mystery. Allied to this fact is the principle that as an
independent and fully recognised Order we seek to adhere to the real Martinist tradition of
conducting ourselves for the sake of Christ and to the service of the human community in his
Name, which really precludes all self aggrandisment and vain glory. Therefore, the main purpose
of this very short paper on our antecedents is aimed at the current membership to fully foster
awareness of both the parentage and the conception of the Order and to elicit a sense of belonging
to this prestigious bearer of spiritual lineages from France for our individual Martinists

In order to fully understand how the formation of our Order came into being as Grand Master I
will recall the personal elements of the historical framework as it then existed in order to
demonstrate the connections and the serendipity which blessed the relationships that initially
created the MOUP.

\subsection{Personal Contact}

While living in the U.S.A in 1989 I was asked to act as a liaison officer between the Belgian
Grand Priory of the C.B.C.S. and its U.S. counterpart. It was through this relationship that I first
came into contact with Marc Jones. At that time he was acting Marshall of the French Speaking
R.E.R. Lodge of Saint Omer where I was invited to become a member of the C.B.C.S. of the
Belgian Grand Priory in 1990.

Over a number of years in which I got to know Marc Jones through our mutual Masonic
connections, I discovered that he was among other things the Grand Master of the Ordre Martiniste
S.I.; based in Luxembourg. The OMSI is an Independent and fully recognised Order whose
antecedents are found in the Ordre Martiniste of which Papus was the acknowledged founder.
Papus is also the founder of modern Martinism which he set up and whose distinct spiritual
imprint is very visible and still exists today in true and regular Martinist Orders.

At that time, I was a member of the Hermetic Order of Martinists, (HOM) which was a completely
independent offshoot of the Ordre Martiniste Et Synarchy (OMS) restricted to Master Masons and
members of the Societas Rosicruciana In Anglia. The important element of joining O.M.S.I to me
was the fact that it was of mixed membership which is the basis of traditional Martinism. It also
had amongst its filiations a very important line of filiation through a remarkable French Martinist
named Constant Chevillon of the Ordre Martiniste de Lyon. Constant Chevillon was a mystic, a
Bishop in the French Gnostic Church, Grand Master of the Ordre Martiniste, and Martyr to the
Martinist cause during the Second World War who was assassinated by the Vichy Regime, hence
the spiritual importance of this line to me as a follower of that path.

\subsection{Creation of a Martinist Order}

Following a number of discussions regarding the introduction of the O.M.S.I into England in
particular and Great Britain in general, it was mutually agreed and ratified by all involved to open
OMSI Chapters and in 1995 this was achieved by the setting up of the London Chapter.
Subsequent Chapters were chartered and this expansion eventually evolved into a Province created
on the 16th September 1997, at which time I was appointed Sovereign Provincial Grand Master
and Legate of the Ordre Martiniste S.I. for the United Kingdom.

In the latter part of 1998 tensions between the Province of the United Kingdom and The Grand
Master of the O.M.S.I came to a pitch resulting in a temporary cooling of relations over a number
of issues of which the majority were of an administrative nature. The actual History of Martinism
is replete with this dynamic of change and many examples of the creation of major Martinist
orders may be found as a parallel.

In order to seek the freedom of expression to continue to operate in a responsible and independent
manner this resulted on the 13th day of February 1999 in the creation of a new Sovereign Martinist
Grand Lodge being formed called the Martinist Order of Unknown Philosophers, of whom the
three primary signatories to the Charter were Michael Norman Buckley, Grand Master, John
Roger Paternoster, Deputy Grand Master, and John James Morgan, Assistant Grand Master and
acting Grand Recorder.

This action created the need for a re-establishment of fraternal lines of transmission and
recognition and as a result within a relatively short period of time this was achieved by the signing
of a Concordat between the Grand Prior Marc Jones of the International Grand Priory of
Martinism-Martinezism and The Grand Prior Michael N Buckley of Grand Priory of
Martinism-Martinezism of Great Britain on the 21st September 2002, in London.

\subsection{Concordat(s)}

The effect of this Concordat was to afford recognition and re-establish the close links and common
affiliations that both Orders possessed and to allow freedom of inter-visiting which had been
banned up to that time; subsequent Concordats of a similar nature have been signed with other
recognized Martinist Orders. 

Success, as always, is seated in the providence of the Divine and we look to a future where in we
serve with peacefulness and continuity in the work of re-integration for the whole human
community.

\textbf{Brighton, 11th November, 2017}