\section{Marrakech Convention --- Important Q's \& A's}

\faq{What is a ``free'' Martinist?}

A Martinist is someone who is a member of the Martinist ORDER. One becomes a Martinist through being inducted by another Martinist who has the proper qualifications and authority to confer The Initiation. A person who is a member of the ORDER is called a ``Martinist'' and as a Martinist he/she is expected to live the Martinist life, i.e. work towards his/her regeneration and ultimate reintegration. Martinists come together and form groups and these groups are called Lodges. A Martinist does not have to become a member of a Lodge—but may certainly do so if he/she would like to participate in Lodge activities. \textit{A Martinist who is not a member of a Lodge is called a ``free'' Martinist.} A ``free'' Martinist may visit a Lodge on the invitation of the Lodge Master, however if he/she would like to attend the Lodge regularly it would be proper to apply for membership in the particular Lodge. Living the Life and striving towards regeneration and reintegration is an \textit{individual work} --- whether one chooses to become a member of a Lodge or prefers to remain ``free.''

\faq{What are the tenets of the ``Martinist Doctrine''?}

Very succinctly:

\begin{enumerate}[label = (\alph*)]
	\item Original Man (also known as Primitive Adam or Archetypal Man)
	was a composite Spiritual Being, emanated by God to fulfill a particular mission. He dwelt
	on a high spiritual plane where he enjoyed many privileges. 
	\item Through the misuse of his free will, he ``sinned.'' His error brought about his fall
	from his pristine position into the physical world. He was originally a unified Being, but in
	his fall he became shattered and scattered…the cells that originally composed him now form
	the souls of the men and women who people the physical world (Humanity).
	\item His place was taken by another Being who elected to do his work and, in
	addition, to show him the way back to his First Estate. This Being is known to Martinists as
	Ieschouah (yea-hesh-shoe-wah). 
	\item The task of humanity, individually and collectively, is to become reintegrated into
	the Archetype again, so that Primitive Adam may be restored. Until we are reintegrated, we
	will continue to suffer the consequences inherent in the physical world (called the ``Forest of
	Errors'' by Louis-Claude de Saint-Martin). 
\end{enumerate}

\faq{What is the ``Way of the Heart''?}

The head is the center of the Intellectual Self. The heart is the center of the Emotional Self, or of the love nature. To follow the ``Way of the Heart'' is to live a life characterized by kindliness, compassion, charity, humaneness, forgiveness, benevolence, understanding\ldots

\faq{Can a person be a Martinist if they have not been inducted by an Initiator?}

No! And I''m glad you asked because there are some people who have been sent ``do-it-yourself'' instructions by a certain correspondence school wherein they are directed to utter some words and tap themselves on their heads with some object such as a stick. After having done this they send a ``report'' to the school and in return they receive a ``membership card''! These unfortunate people are then misled into believing they are Martinists! Please be always cautious of people you meet who say they are Martinist…if you ever meet anyone who has been misled as a result of such fraudulent practices, please in love direct these innocent masqueraders to the true Light. 

\faq{What is the purpose of a Martinist Lodge?}

A Martinist Lodge is composed of persons who are Martinists and who meet for the purposes of Martinism. Papus organized the Martinist Order to secure and ensure the perpetuation of The Initiation and this remains the first work of the Lodge. Our order exists to restore Man to his pristine power. If this is to be accomplished the Lodge must be exceedingly active—members should diligently scout for suitable candidates throughout the length, breadth, height and depth of society and lead them to the Lodge where, if they are determined to be worthy, they may be inducted as free Martinists and provided with the basic teachings which will start them on the way to Regeneration and Reintegration. 

\faq{Should all Martinists become members of a Lodge?}

Whereas all Martinists are expected to live the Martinist life --- not all Martinists are interested in Lodge work. Free Martinists may visit a Lodge on the invitation of the Lodge Master --- and if they identify with Lodge work they may apply to the Lodge for membership. It is an individual question.

\faq{Is there a connection between the Universal Gnostic Church and the Martinist Order?}

Grandmasters Papus, Bricaud, Blanchard and other eminent Martinists were Bishops of the Universal Gnostic Church which was appointed the official church of the Martinist Order ever since the early days. Both organizations are sovereign and independent; a friendly relationship exists between them. 

\faq{What does ``Rose+Croix'' mean?}

This is a vast subject, and a complete answer cannot be given in the space available here, but in response to the level from which I believe you ask: it is an award, a designation, or a term given by Initiates to those amongst themselves who are recognized as having attained a state or condition of inner or spiritual consciousness. 

\faq{In what sense is the word ``Master'' used by Martinists?}

As ``teacher.''