\documentclass[letterpaper]{article}

\usepackage{geometry}
\usepackage{amsmath,amssymb}
\usepackage{textcomp}
\usepackage{bbding}
\usepackage{pifont}
\usepackage{parskip}
\usepackage{url}


\title{\vspace*{-5em}Worth Commandery \textnumero{} 19, KT\vspace*{-1em}}
\author{List of Committeemen (Draft)}
\date{\vspace*{-1em}\today}

\newcommand{\cman}[4]{\textbf{#1}\hspace*{\hfill}\url{#2}\\\hspace*{\hfill}#3\\\hspace*{\hfill}#4}
\newcommand{\comm}[3]{\section*{#1 Committee\textsuperscript{#2}}The #1 Committee is tasked with #3}
\newcommand{\mand}{\CrossMaltese}
\newcommand{\bylaw}{\Cross}

\begin{document}
	\maketitle
	
	Committees denoted with ``{\small\mand{}}'' are required by the Grand Commandery Knights Templar of Texas, either directly through the \textit{Statutes and Regulations of the Grand Commandery Knights Templar of Texas}, or through the list of committees required as part of our submitted annual returns. Committees denoted with ``{\small\bylaw{}}'' are required by the Bylaws of Worth Commandery. All other committees are deemed ``Special Committees.'' The Commander is assumed to be an \textit{ex-officio} member of all committees, unless legally impermissible.
	
	\comm{Bylaws}{\mand}{reviewing the bylaws of Worth Commandery and updating them as needed, to be submitted to the Grand Commandery, Knights Templar, of Texas.}
	
		\cman{Committeeman \#1 (Chairman)}{arg2}{arg3}{arg4}
	
	\comm{Charity}{\mand}{examining all claims for assistance and award relief as deemed necessary and legally appropriate. This committee always consists of the Commander, Generalissimo, and Captain General.}
	
		\cman{Gabriel Jagush (Commander)}{texanmason@gmail.com}{979--285--4244}{2132 David Drive, Fort Worth, TX 76111}
	
	\comm{Educational Foundation}{\mand}{advertising and awarding scholarship application opportunities for the Texas Knights Templar Educational Foundation, and assisting students with their scholarship applications to the same.}
		
		\cman{Committeeman \#1 (Chairman)}{arg2}{arg3}{arg4}
		
	\comm{Finance}{\bylaw}{auditing the books of the Worth Commandery Treasurer, reporting the results to the Commandery, and assisting with the annual returns of the commandery. \textbf{For practical purposes, the chairman and other two committeemen will be appointed immediately prior to the stated conclave at which they are needed to report.}}

	\comm{Knight Templar Eye Foundation}{\mand}{raising awareness of the Knight Templar Eye Foundation (KTEF), developing fund-raisers to benefit KTEF, and developing plans for Worth Commandery to be better represented as an organizational donor to KTEF.}
	
		\cman{Committeeman \#1 (Chairman)}{arg2}{arg3}{arg4}
	
	\comm{Membership}{\mand}{recruiting Master Masons to become members of the York Rite, assisting and encouraging Sir Knights in the process of reinstatement, and raising awareness of Commandery as a worthwhile fraternity.}
	
		\cman{Committeeman \#1 (Chairman)}{arg2}{arg3}{arg4}
	
	\comm{Patriotic \& Civic Activities}{\mand}{working with past and present members of Templar District \textnumero{} 6 Color Guard to conduct flag presentations, arrange parade appearances, and coordinate with local organizations that would like Templar representation at their events.}
		
		\cman{Jerry Taylor (Chairman)}{jwade284@swbell.net}{817--706--2255}{arg4}
		
	\comm{Publicity}{\mand}{working alongside the Membership Committee to advertise and recruit for Commandery, raising awareness of Worth Commandery's philanthropy, and increasing our visibility in North Texas.}
	
		\cman{Ricky Cox (Chairman)}{rcox70@gmail.com}{817--229--4797}{499 Skyview Lane, Azle, TX 76020}
	
	\comm{Sickness \& Distress}{\bylaw}{keeping an eye out for our members who have not been able to make it to Conclave in a while, visiting home-bound members or members in the hospital, sending ``get well soon'' cards, and so forth.}
	
		\cman{Committeeman \#1 (Chairman)}{arg2}{arg3}{arg4}
	
\end{document}