\documentclass{article}

\usepackage{
	geometry,
	multicol,
	parskip,
	url
}

\geometry{margin = 0.5in}

\setlength{\columnseprule}{1pt}

\title{\vspace*{-3em}Grand Master's Fund Jewel}
\author{Grand Council Conference (Arlington)}
\date{\today}


\begin{document}
	\maketitle
	\pagenumbering{gobble}
	%\begin{multicols*}{2}
		There are three things that I think about when I think of the No Mason Left Behind program:
		\begin{itemize}
			\item The North-East Corner
			\item ``I am my brother's keeper.''
			\item ``On yonder book, that oath I took.''
		\end{itemize}
		The Grand Master's Fund is a charitable project that the Most Illustrious Grand Council of Royal \& Select Masters of Texas started this past December at Annual Assembly. The Grand Master's Fund is our way of contributing to the No Mason Left Behind program. Each purchase of a Grand Master's Fund Jewel will go the No Mason Left Behind program. Now, because the Texas Masonic Retirement Center is the official charity of the Grand Council, most of us here are familiar with No Mason Left Behind, but in case you're not familiar with the program, No Mason Left Behind is a program that helps secure housing and care at the Texas Masonic Retirement Center for Master Masons and Widows who could otherwise not afford it.
		
		``It might have pleased the great Creator of heaven and earth to have made man independent of all other beings; but, as dependence is one of the strongest bonds of society, mankind were made dependent upon each other for protection and security, as they thereby enjoy better opportunities of fulfilling the duties of reciprocal love and friendship.'' That's from the Beehive portion of the Master Mason's lecture, and it's exactly what we're talking about: protection and security.
		
		Most of us here know one or more folks that have directly benefited from the No Mason Left Behind program. It is, in every sense, a life-saver. That's why we care so much about the program. When sales began for the Grand Master's Fund Jewels, Companions flocked to the tables. By the time Annual Assembly finished, the Cryptic Companions of Texas had raised over fifteen thousand dollars in less than thirty-six hours. The jewels are already completely paid-for. There are 27 ``Founder's Jewel's'' which were purchased at a higher cost which funded the purchase of the rest of the jewels. Because of this, your purchase goes directly to the program.  
		
		The form to buy a Grand Master's Fund Jewel is easily accessible on the Grand Council website.  Head to \url{http://www.yorkritetexas.org/council/} and look for the menu item, ``Grand Master's Fund Jewel.'' That page will lead you to a PDF form that you can print out and mail to the Grand Recorder's office. Each jewel is available for \$150.
		
		We can all make a difference. The motto of the Grand Master's Fund program is ``For the Benefit of Future Generations,'' and that's something we intend to live by. Thank you for your support of Cryptic Masonry, for your support of the Grand Council, and most importantly, for your support of the No Mason Left Behind Program.
		
		%\vspace*{\fill}
		%\columnbreak
		\begin{itemize}
			\item 3 Things - No Mason Left Behind
				\begin{itemize}
					\item The North-East Corner
					\item ``I am my brother's keeper.''
					\item ``On yonder book, that oath I took.''
				\end{itemize}
			\item GMF started by GCRSMTX in December
			\item Benefits No Mason Left Behind
			\item Explain No Mason Left Behind \& the TMRC.
			\item Beehive snippet
			\item Protection + Security
			\item ``Life Saver''
			\item \$15,000 raised in less than 36 hours
			\item Jewels already paid-off (no overhead)
			\item \url{http://www.yorkritetexas.org/council/}
				\begin{itemize}
					\item ``Grand Master's Fund Jewel''
					\item PDF to mail
					\item \$150
				\end{itemize}	
			\item ``For the Benefit of Future Generations''
			\item Thanks
			\item Questions?
		\end{itemize}
		%\vspace*{\fill}
	%\end{multicols*}
\end{document}