\documentclass[b6paper]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[super]{nth}
\usepackage{parskip}
\pagestyle{empty}

\newcommand*{\newentry}[3]{\pagebreak{}\section*{#1 \nth{#2}, #3}}
\newcommand{\ldl}{\emph{Lumen de Lumine} exercise}
\newcommand{\mvp}{\textit{Martinist Visualization \& Prayer}}
\newcommand{\hol}{\textit{Heart of Love} exercise}
\newcommand{ \eoe}{\textit{Exercise of the Egregore}}
\newcommand{\pms}{Past Masters}
\newcommand{\col}{\textit{Chain of Light} exercise}

\begin{document}

\section*{December \nth{5}, 2019}
	
Quick meditation log for Thursday, December \nth{5}. I skipped yesterday because I was not feeling well. I took a sick day from work and everything. I don't feel guilty about that. Starting again today. Working on Exercise D, being aware of my presence and living.

Physical sensations that I noticed were:
\begin{itemize}
	\item I'm dehydrated.
	\item The pleasantness of sitting still.
	\item I'm hungry.
	\item I noted the presence of the mask on my face. Not in a spiritual way, but taking stock of how it physically feels on my face.
	\item Enjoying the smell of incense.
\end{itemize}

Intrusive thoughts that I experienced:
\begin{itemize}
	\item Worries for my health.
	\item A sudden and intense desire to find and see a doctor to go get a check-up. It wasn't a sensation of being sick, just of desiring a status update on my health.
	\item Dissatisfaction with my weight.
	\item MOUP as an organization. Wondering how it works. How the finer details work. How does one ``exchange initiations?''
\end{itemize}

Heart of Love Exercise:
Phase 1 (Mother Mary) was very peaceful, very pleasant. This carried over to Phase 2 (my wife). I really like Heart of Love. It seems like it fills me with a sense of peace that I didn't know I was missing.

\pagebreak

\section*{December \nth{9}, 2019}

Around 7 AM. Just finished meditating. I have missed a couple of days. I have had a \textit{ripping} sinus headache for the past few days. It might actually be a sinus infection. Sarah is trying to take care of me as best as she can. Because of that, up until today, I have not felt well enough to even sit down and concentrate, because the pain has been so bad that I can't even sit still and think, or try not to think, if we're talking about meditating.

I sat down and did Exercise D. Taking stock of physical sensations, trying to be aware of being alive. It helped a lot. One of the things that I noticed was that in the same way that kids can learn to squirt milk out of their eyes, I could feel air passing in and out of my tear ducts because my sinuses are so messed up. Overall, Exercise D went well. I had a couple of interrupting thoughts. One was was ``Who am I?'' to which the response was ``I am Sarah,'' which was a really pleasant sort of realization, especially because I'm experiencing some unequal yoking with her right now, because I'm sick and she's taking care of me, and I'm feeling guilty because I'm not doing anything around the house or contributing. So, ``I am Sarah,'' is very comforting. 

Another intrusive thought that I had was ``I forgive Lance.'' Lance Kennedy is a guy who I have some compunctions with because he really likes the (former) Spanish dictator Fransico Franco, who killed a bunch of my relatives. The realization that I had was, ``I forgive Lance.''

I had some intrusive thoughts about some masonic things that we have coming up. I am very excited about Grand Chapter, and I'm very excited about Texas MasoniCon. I had some realizations along the lines of ``oh, crap, I need to take care of X, Y, and Z!'' However, these were relatively low-key intrusions.

\pagebreak{}I did the Heart of Love meditation with Mother Mary. It was a lot calmer than before --- very pleasant. I \textit{did} have a lot of trouble concentrating because of the sinus pain. Again, Phase 2 with Sarah, very pleasant, very loving. I introduced Phase 3 for the first time because this is the third week of doing the Heart of Love. This is focusing on someone who challenges us. I chose someone who I used to consider a friend, who has shown that he's maybe not as good of a friend as I thought he was, and it was \textit{really difficult,} and kind of upsetting. I got sad and upset, and I was choking up. I was having a rough go of it. I lasted about three minutes with this phase before I had to stop. It was affecting me very strongly. Maybe that's part of it --- it's supposed to draw these feelings out of me. I get repeating ``I love you'' in my head because I feel like I still do love this person, but it hurt to connect with them in this way.

During the Martinist Prayer \& Visualization, I prayed for my buddy Billy. I felt very strengthened by this and I hope he felt the same.

\pagebreak

\section*{December \nth{11}, 2019}

Yesterday was very frustrating. I got up early, but I didn't get up early enough. The entire time I tried meditating, I was consumed by thoughts that I should have gotten up earlier, I should have done this, I should have done that, I'm running late, etc. A totally worthless session. Earthly thoughts.

Today's meditation was a lot better. I'm on schedule, or at least, not terribly late. I did the introductory Exercise D. I'm getting a lot better at focusing on physical sensation and focusing on the living process of my body, and being present, without letting things in. I did have some pervasive thoughts, which were mostly related to the thoughts of my sinus infection/illness. Still present in the moment, I guess, but planning too much.

I did the Heart of Love meditation today, and I really needed it. It's one thing to walk into Heart of Love and being sharing your heart and sharing this love, but there are some days when you wake up and pray, ``please, I need this love.'' I found myself almost begging the other participants in the exercise for their love. Very humbling. Phase 3 was very difficult again. This person is someone who I love dearly but who I butt heads with all the time. He's going through a really tough time right now, and only just yesterday, has been lashing out a lot. I prayed for him and his wife, and their unborn child. I really love the guy, and he does challenge me. It was very moving in a raw sort of way.

\pagebreak
\section*{December \nth{19}, 2019}

Today was proof positive that meditation that is not like riding a bicycle. It's not something that you maintain without practice. It's more like working out. If you don't do it, you're going to have a hard time when you come back. I'm only just now feeling better after my sinus infection. I'm not ``100\%'' but I'm ``85\%--90\%'' (My wife is almost recovered). I jumped back into the chair to meditate, started doing all the work that I've been doing, and was pretty much immediately humbled. It was really challenging. I haven't done this in a week and I need to do it all the time. That's fair. In comparison to the past, when I was meditating regularly as part of my relgious and martial arts practice, it's different. It is what it is. I am glad that I have the opportunity to improve, and I'm glad that I'm mostly feeling better.

I had a lot of challenges with the ten-minute meditation, which wasn't surprising. I was preoccupied with earthly thoughts and felt kind of lost. The Heart of Love exercise went okay, and I added in Phase 4 (meditating on cardiac union with the whole world). Phase 4 makes me want to actively love the world more. I know in my head that I'm supposed to love the whole world, but this exercise is really making me \textit{feel and want} that truth in my heart. It's very pleasant. My desires really are starting to line up with Martinist and Christian teachings on a more fundamental level. I'm finally going from ``I \textit{should} do this'' to ``I \textit{want} to do this.''

\pagebreak
\section*{December \nth{20}, 2019}

Just finished doing the standard 10-minute introductory meditation. Had some intrusive thoughts --- nothing terribly severe. I had some excited thoughts about stuff I'm doing in my professional, personal, and masonic life. I got excited about Commandery, about getting my ears pierced, etc. I had one intrusive thought that was more of an epiphany than any of the others: Fear is a form of suffering. Initially, it came into my mind as ``FEAR, SUFFERING, FEAR, SUFFERING, FEAR, SUFFERING,'' so I echoed back, as a sort of question, ``fear, suffering?'' The response I got back was ``fear is suffering.'' I echoed back (again), ``fear is suffering?'' and the response was ``fear is a \textit{form} of suffering.'' That's very true, in my opinion. I know that I suffer from fear, and that many people I love suffer from fear, and it explains a lot of behavior.

\pagebreak
\section*{December \nth{25}, 2019}

It's Christmas evening! I'm winding down for the night. I just finished my first meditation in five days. I have been slacking. It's proof that you need to do it every damn day. Christmas season just kind of got a hold of me, and here we are. It was an okay meditation. Not the best, not the worst --- just kinda there. It was pleasant. I experienced excitement over seeing my cousin today, I thought about my District Deputy duties for the Grand Council, and I also experienced some physical challenges from accidentally burning \textit{far} too much incense. However, for the most part, it was nice.

I had a mental image of myself pushing a refrigerator through the forest. I'm not sure what that means.\footnote{On December 30, 2019, I had a conversation with Elisha mentioning this imagery. After the conversation, I am inclined to think that it's about a metaphorical effort to shove a square peg into a round hole. What is it in my life that I need to stop trying at, or redirect my efforts from? It could also mean that I am just trying to accomplish a difficult task, which I would much rather believe. However, Elisha seems to think that it's the former rather than the latter.} Sysphean efforts, perhaps. The Heart of Love meditation went well. I focused on Saint Francis of Assisi for Phase 1, and my cousin for Phase 2. Phase 3 focused on someone who I really want to love, but am struggling to. Phase 4 went just fine.

Did the visualization and prayer with my cousin as a focus. I hope it helped/helps him --- he needs help.

\pagebreak
\section*{December \nth{26}, 2019}

Back to work today. Got up early (not early enough). Had a much more successful meditation than last night. Still had a bunch of disracting thoughts, but overall it was very good, and I was better able to focus on my breath, and be more present and in the moment. One of the challenges that I had was that my dogs were barking a lot. I have a fear response that is associated with my dogs barking because they're good watchdogs, and we don't live in a great neighborhood. I had to calm myself down, and tell myself that I was experiencing is a experiencing a fear response and disassociate myself from the idea and emotion. 

My Heart of Love meditation experience was heart-warming and joyful. I did stage 3 with my boss at work, whom I like and perhaps even love, but who is pretty challenging at times. I prayed for our Aunt Darla. She recently lost her husband and I don't know why I haven't prayed for her sooner, to be honest.

\pagebreak
\section*{December \nth{29}, 2019}

It's been two days since I meditated. This was a much better meditation session than last time, although I did have some issues focusing and maintaining concentration, but nothing out of the norm. I was excited about things that will happen later today --- going to church on the First Sunday in Christmas, seeing an old friend, and so forth. My lack of concentration was not ideal, but I'm not terribly mad about it, because I am excited. I'm just trying to remember to take note that I'm experiencing these thoughts as they pass through my brain, and be mindful.

The Heart of Love meditation went alright. When I performed Phase 1 of the HoL meditation, I prayed the \textit{Angelus}, which is a four-line prayer that uses the \textit{Hail Mary} as a repeated refrain. I feel that it intensified the meditation significantly. For Phase 2, I chose my wife as I normally do, because she's a very familiar subject for this phase. I'm trying to pick familiar faces/subjects just to get back into routine. I don't need ``revolutionary'' right now, I just need ``consistent.'' During Phase 3, I had a visual of my subject and I blowing on embers in each other's heart, which I thought was really interesting and beneficial to the meditation. I liked that a lot. Still struggling with Phase 4 a little, since it's visualizing a cardiac union with the entire world, but it's pleasant and I enjoy it.

Prayed for my buddy's wife. She's pregnant with the successful results of in-vitro fertilization and we're really hoping this goes great for them.
 

\pagebreak

\section*{December \nth{30}, 2019}

Disappointing session today. Just a whole lot of nothing in terms of capability today. Yesterday was really good --- I don't know what happened today. I had some intrusive thoughts today, not a lot. I'm slightly preoccupied with my left earlobe. I got my ears pierced a little while back, and it seems to be healing oddly. That wasn't was big deal, though, as it only lasted a few seconds. Thinking about babies. My buddy's expecting his first soon. Been praying for him and his wife. Fairly standard 10-min meditation, though.

When I attempted the Heart of Love meditation, it was frustrating, annoying, strange, and disappointing. Try as I might, I was not able to get my heart to light up in the meditation. I just couldn't. I tried with the first three phases and got a big fat zero out of it --- I didn't even bother with Phase 4, as I didn't see the point. I have never experienced anything like this and I really didn't like it.

\pagebreak
\section*{December \nth{31}, 2019}

Back in the saddle again. Don't know exactly what the hell happened, but it was kind of cool. Half-way through the ten-minute meditation, things got strange. Up until then, I had been having some intrusive thoughts about another Martinist body that resides within Texas --- the Ordre Martinistes Souverains. I thought about the guy who runs it, too. Tried to just catalog \& dismiss the thought. After that, I experienced a strange thought pattern around the feasibility of burning incense in a lodge building without triggering the smoke detectors. Super trivial stuff --- ``oh, hey, I'm experiencing this thought, NEXT PLEASE!'' Once I am able to identify that I've gotten stuck in a thought pattern, dismissing it is fairly simple, but the challenge I have is recognizing that I'm in a thought pattern in the first place. Half-way through the meditation, I experienced a very strange smell. I had been burning Palo Santo, which has a distinct, smoky sort of smell. However, I began smelling this floral scent. My first thought was of surprise, as Palo Santo burns out fairly quickly and does not smolder long. This wasn't Palo Santo, though. It was floral, bright, and sweet. I smelled a lot of other stuff in the scent that I couldn't identify. It might have smelled a bit like a confectionery or sweet shop (but not like a bakery). Super great experience. 

Once I finished the 10-minute meditation, I launched straight into the Heart of Love meditation with no problems at all, completely unlike yesterday. My heart lit up instantly. I spent very little time on each phase because each phase felt ``complete'' very rapidly. I then prayed for my friend Billy during the Martinist Visualization \& Prayer.

\pagebreak{}After my ``work'' was done for the morning, I examined a candle that I had sitting on the desk. I had been concerned that this candle was creating a false positive of sorts, as it was cast with cinnamon, oranges, etc. However, the scent from the candle was so weak I actually had to nose the candle like a brandy snifter, and even then, the aroma profile of the candle was totally different from the smell I experienced during meditation. I don't know what this was.

I find it curious that this occurred the morning after a phone call with Elisha, when I stated that I had not experienced anything strange while meditating for a while now. He specifically asked about experiencing smells, and I responded that I hadn't encountered any. I am willing to accept that this may have been the power of suggestion, but it was so strong and powerful that I would rather accept that this was a function of the egregore. Perhaps it was the Past Masters rewarding or encouraging me after an absence of visits with my mentor?

\pagebreak{}\section*{January \nth{2}, 2020}

I have just completed my morning meditation. It was a shorter one than normal. The active portion of the meditation with the \textit{Heart of Love} exercise and the \textit{Martinist Visualization \& Prayer} was about the same length as it is always, but I cut down the introductory meditation from ten minutes to five just because I didn't get my butt in gear when I needed to. I had an okay session. My computer fan was creating some noise, like a periodic clicking sound. I decided to use that to my advantage and use that as a timer to time when I breathe in, when I hold my breath, when I breathe out, and when I keep an empty breath. That was kind of nice. 

The intensity of the meditation was seemingly not affected by the shorter introductory meditation. I would prefer to have a longer introductory meditation for the sake of self-discipline, but this was encouraging. I didn't notice anything strange during this session.

\pagebreak{}\section*{January \nth{6}, 2020}

Just finished my morning meditation. It went okay. There was nothing particularly revolutionary about the 10-minute introductory meditation.  I had distracted thoughts about my lodge and about my computer which was in the background making noise. The distracted thoughts about my lodge weren't bad ones --- they were just interfering. It was a so-so meditation session in regards to the preliminary meditation.

When I did the first phase of the \textit{Heart of Love} meditation, I was originally going to meditate with the Virgin Mary as I have been doing regularly, but at the last second, I realized I wanted to meditate with Fred Rogers of the Mister Rogers show. He was a Presbyterian minister for a long time, and he was/is an exemplar of what it means to love unconditionally with the pure heart of a child. Strange, I know, but it made sense after I thought about it for a bit. My heart lit up. I felt like a little kid again and it was amazing and very different from what I was expecting. For phase two, I was going to meditate with my brother, but I had this internal thought that interrupted me, almost loudly in my head, ``no you're going to meditate on with him for phase three, which is people who challenge you instead.'' It was not a voice, but almost like a thought that felt external to me, which I thought was interesting. I also prayed for him during the \textit{Martinist Visualization \& Prayer}

\newentry{January}{9}{2020}

I've been laid up for a couple of days. I've had some pretty bad lower back pain --- almost to the point where I can't walk. No explanation yet, but the nurse practitioner that saw me says he thinks it's a lower back sprain. This has been messing with my ability to meditate and concentrate, because of the pain.

Sitting comfortably has been a challenge, but today I felt well enough to meditate again, and I integrated the \textit{Exercise of the Egregore} into my meditation curriculum. I'm not sure if I got into the program at the right time to start doing the \textit{Lumen de Lumine} exercise since it's tied to the cycles of the moon. I will check and see, and maybe tonight, I'll be able to do it. I don't know, as that just depends on my pain level.

Today during meditating, I had a lot of distracted thoughts that were related to my back pain, which was unfortunate, because even with my neck pain that has not been an issue, or has only occasionally have been an issue. However, I did the \textit{Exercise of the Egregore} and it was very good. It actually went very well, and I was kind of surprised by how, just through being initiated, how many members of the Martinist Order that I actually do know.

I prayed for Jack. In summary: difficult first half, enjoyable second half.

\newentry{January}{10}{2020}

I just performed the \ldl{} for the first time and I thought it was super interesting, albeit kind of procedurally complicated. I think that has just more to do with me never having done it before --- I was definitely pretty confused at times. I jumped-started part of it before I should have, and then I had to put some candles out and go back to the proper step before going back and lighting the candles again. I felt a little odd, sitting in a circle of candles. It didn't help that I didn't do the exercise correctly at first! I performed a five-minute introductory meditation to try and clear my mind. I had to remind myself fairly often to try and catalog my intrusive thoughts instead of pursuing them.

I performed the \eoe{} and I have decided that I like it very much. It's cool to to visualize everyone, and be with everyone. It almost feels like everyone is actually there, though I suppose that's the entire point of it. I then performed the \ldl{} and opened myself up to any thoughts that I might experience, or any visions that I might see. I had a very vivid mental image of black smoke rushing towards the circle of lights, which was then buffeted away by some sort of invisible wall.

In the same vein, I experienced a strong visualization where I was in the basement of my old home in Germany. That basement was kind of a scary place. I don't think anything bad ever happened there to me, but as a kid, I was always afraid of it. It was always dark, always spooky, and always had a dark aura to it, although that may have been entirely my imagination. I disliked the whole place with the exception of my father's workshop. I was afraid of the whole basement, unless I was in the workshop, I would always close the door from the workshop to the rest of the basement. Even then, unless I was there with my dad, or with my brothers, I still felt uneasiness. This sensation even included the laundry room. I didn't feel comfortable. It was one of the largest basements I've ever seen in my life and it was just a place that I associate(d) with fear.

I had a vivid mental image of a man in a padded cell who realized that he was afraid of restraints and confinement. The guy in the cell didn't look like me at all, but in a sense, he was me. I think that's very accurate. I already know I'm afraid of having my life being confined and restrained; this is not a surprising mental image.

After that, I experienced a general fear of pain. I'm afraid right now. I'm in a lot of chronic pain, and I'm very afraid that it will never go away, because it's been with me in some form or another for a very long time, whether it's my neck, or my back, or my knees, or the nerve damage in my hand. All of my joints are messed up; I'm always I'm afraid that this pain will never end.

It was a lot of fears. Definitely a lot of fears and discomfort, but it was not an uncomfortable \textit{experience}, though. It was almost as if the Past Masters were trying to vividly call attention to things that I am suffering from in terms of fear, because that's what fear is --- fear is suffering. It feels like a statement: ``Pay attention to these things now.'' Why are the \pms{} calling my attention to my fears? I don't know, but I'm going to make a note of it. 

This was kind of technically the last day that I could do the \ldl{}, because tonight is going to be the full moon. Emblematically, I'm going to say that the moon is still waxing until moon rise tonight, since it's the morning now. I've got ten hours at least, if not more, because it's about seven in the morning now that I'm finishing up the meditation and journaling. For the purposes of this exercise, the moon is still waxing --- just barely. I'm looking forward to doing this in another three months or so, when I'm scheduled to do it again.

\newentry{January}{12}{2020}

This was not a particularly successful session of meditation. I am meditating, or was meditating, in the evening. I am closing up my day, and getting ready to wind down. The problem with this, is that my physical tiredness has altered my mental state, and my alertness is shot. I was not able to maintain concentration reliably during my warmup routine. My ability to visualize was not functioning well. I'm going to try again in the morning, but this was not great.

\newentry{January}{13}{2020}

Excellent meditation session this morning. I got up early, I made myself a cup of coffee before meditating, and I got to work. I feel that the coffee beforehand actually helped. Today, I did a 10 minute introductory meditation, the \eoe{}, and then performed the prayers listed in the \col{} and then performed the \mvp{} for my buddy Jack.

During the \col{}, I read the \textit{Prayer of the Elect Cohen}, I recited the \textit{Lord's Prayer} from memory, I read \textit{Psalm 91}, I read the \textit{Prayer for Peace}, and I recited the \textit{Gloria Patri}. I really, really liked this exercise. It ties in very strongly with my background as a member of the Episcopal Church. It just feels very familiar, and it's very pleasant. When I was doing the introductory meditation, halfway through I felt a sense of great peace. Mind you, I still struggled with distractions and thoughts that ran through my head, but the sense of deep inner peace that I felt when doing the introductory meditation, which carried over to the \eoe{}, the reading of the prayers, and the \mvp{} was just incredible. I was wonderful. I just really enjoyed the serenity that I'm walking into the day with now whether that's serenity lasts for the rest of the day. I don't know but I appreciate starting the day like this.

During the \eoe{}, when I was visualizing Martinists past and present, I had an interesting experience in which, while calling up the memory and visualization of the different Martinists that I know, and placing myself in the crowd, I saw the blue flash which I have recorded earlier in this journal. It sat in the crowd with me. I feel that that was probably a Past Master of some kind.

\end{document}